Changelog

### 2021-05-22 Chapter-2/Chapter-2.tex

The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the simple modular exponentiation algorithm function in many algorithms (Diffie-Hellman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that cryptography libraries usually have several implementations for some ciphers.
For example, AES can have more than five different implementations in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side-channel mitigated versions. However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA). These ciphers have a lot of big number calculations. It is hard to implement those calculations to be completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers. There are two common countermeasures to mitigate side-channel attacks in cryptography libraries. The first approach is to adopt constant time operation when computing the secret data.  It is hard to migrate all the code into a constant-time implementation. The second approach is to use blinding to obfuscate the information that an attacker can retrieve. Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself. Binding values can alter the input to some unpredictable data and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.

@@

\subsection{Software Countermeasures}
\subsubsection*{Software Vulnerability Identification}
There are several existing works on side-channel leakage detections. According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

@@

\subsubsection*{Runtime Behavior Randomization}

\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
\subsubsection*{Randomization}

\section{Quantification}
Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
of the information are leaked, the program is called non-interference. 
McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. They model the possible information leakage as a network of limited-capacity
channel. After that, they use the maximum rate of the channel to represent the amount of secret information that the execution can reveal.
Backes et al.~\cite{5207642} propose an automated method for QIF
by computing an equivalence relation on the set of input keys. However,
the evaluation shows the approach only works on small programs.
Besides, their approach cannot handle programs with bitwise operations.
However, such bitwise operations are quite common in cryptographic libraries.
Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure a program is non-interference. They adopt an over-approximation method to estimate the total information leakage, and their method
does not work for secret-dependent memory access side-channels.
Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst-case leakage. They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior.
It symbolically reasons about cache
behavior and estimates the amount of leaked information based on cache miss/hit.
Their approach only scales to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} assesses the sensitive level
of side channels with different granularities. It can also analyze side channels in real-world cryptographic libraries.

>>>>

The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the simple modular exponentiation algorithm function in many algorithms (Diffie-Hellman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that cryptography libraries usually have several implementations for some ciphers.
For example, AES can have more than five different implementations in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side-channel mitigated versions. However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA). These ciphers have a lot of big number calculations. It is hard to implement those calculations to be completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers.

@@

\subsection{Software Countermeasures}
\subsubsection*{Software Vulnerability Identification}
For many software countermeasures, the first step is identifying side-channel leakages in software manually. It can be done manually or by some program analysis tools.
There are several existing works on side-channel leakage detections. According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

@@

\subsubsection*{Software Patching}
There are two common countermeasures to mitigate side-channel attacks in cryptography libraries. The first approach is to adopt constant time operation when computing the secret data.  It is hard to migrate all the code into a constant-time implementation. The second approach is to use blinding to obfuscate the information that an attacker can retrieve. Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself. Binding values can alter the input to some unpredictable data and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
\subsubsection*{Randomization}

\subsection{Discussion on Existing Countermeasures}
\section{Information Quantification}
Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
of the information are leaked, the program is called non-interference. 
McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. They model the possible information leakage as a network of limited-capacity
channel. After that, they use the maximum rate of the channel to represent the amount of secret information that the execution can reveal.
Backes et al.~\cite{5207642} propose an automated method for QIF
by computing an equivalence relation on the set of input keys. However,
the evaluation shows the approach only works on small programs.
Besides, their approach cannot handle programs with bitwise operations.
However, such bitwise operations are quite common in cryptographic libraries.
Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure a program is non-interference. They adopt an over-approximation method to estimate the total information leakage, and their method
does not work for secret-dependent memory access side-channels.
Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst-case leakage. They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior.
It symbolically reasons about cache
behavior and estimates the amount of leaked information based on cache miss/hit.
Their approach only scales to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} assesses the sensitive level
of side channels with different granularities. It can also analyze side channels in real-world cryptographic libraries.

### 2021-05-22 changelog.tex
Updates from Overleaf

\section{Requested Changes}

@@

Before the defense, Dr. Wu gave me the following feedback.
\end{enumerate}
\section{Other Changes}

>>>>

@@

Before the defense, Dr. Wu gave me the following feedback.
\begin{itemize}
\item Add a chapter on Discussion and Limitations
\item Discuss potential ways and related work to mitigated reported side channels

I extended the related work on current side-channel defenses in Chapter. I cited and discussed the related work on side-channel defenses from two aspects: software countermeasures and hardware countermeasures. 
\end{itemize}

\item Improve Grammar.
\end{enumerate}
